---
title: "diary1"
author: "Juan Duarte"
date: "2026-04-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_python(here::here("venv", "bin", "python"), required = TRUE)
library(dplyr)
```

## Summary of the project
Study the effect coused by real state property tax in housing prices. We use administrative data to exploit cuasi-experiments in order to identify a causality. Data is mostly georeferenced prices and taxes. The method is a combination between regression discontinuity design and difference in difference.

## This diary
We will narrate the empirical process, by replicating a series of scripts.

## Opening and cleanning raw data.
This python script identify the shapes that are neighbour to each other.
* Loads `gran_stgoPolygon.shp`.
* Translates vectors to degrees in a globe (EPSG:4326).
* Shrinks the polygons to identify the adyacent homogenenous areas (HA)
* Produces pairs of adyacent HA.

```{python, include=FALSE}
import os
import pandas as pd
import geopandas as gpd
from matplotlib import pyplot as plt
import contextily as ctx
import seaborn as sns
import json
import numpy as np
from shapely import geometry
import tqdm
import contextily as cx
from datetime import datetime
from tqdm import tqdm
```

```{r}
config <- list(
    root_dir = normalizePath(here::here())
)
py$config <- config

source_python(here::here("scripts","python", "identify_neighbour_HA.py"))

read.csv("./data_channel/adjoining_HA.csv") %>% head()
```

