---
title: "diary1"
author: "Juan Duarte"
date: "2026-04-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_python(here::here("venv", "bin", "python"), required = TRUE)
library(dplyr)
library(tidyverse)
library(sf)
library(ggplot2)
library(osmdata)
```

## Summary of the project
Study the effect coused by real state property tax in housing prices. We use administrative data to exploit cuasi-experiments in order to identify a causality. Data is mostly georeferenced prices and taxes. The method is a combination between regression discontinuity design and difference in difference.

## This diary
We will narrate the empirical process, by replicating a series of scripts.

## Opening and cleanning raw data.
This python script identify the shapes that are neighbour to each other.
* Loads `gran_stgoPolygon.shp`.
* Translates vectors to degrees in a globe (EPSG:4326).
* Shrinks the polygons to identify the adyacent homogenenous areas (HA)
* Produces pairs of adyacent HA.

```{python, include=FALSE}
import os
import pandas as pd
import geopandas as gpd
from matplotlib import pyplot as plt
import contextily as ctx
import seaborn as sns
import json
import numpy as np
from shapely import geometry
import tqdm
import contextily as cx
from datetime import datetime
from tqdm import tqdm
```

```{r identify-neighbour}
config <- list(
    root_dir = normalizePath(here::here())
)
py$config <- config

source_python(here::here("scripts","python", "identify_neighbour_HA.py"))

read.csv("./data_channel/adjoining_HA.csv") %>% head()
```

This Python script prepares the spatial inputs used to inspect properties near homogeneous-area borders. It:
* loads property coordinates for a selected group of communes,
* converts them into an `sf`-compatible point layer, 
* reads the homogeneous-area polygons for Greater Santiago, and
* extracts the homogeneous area code associated with each role from the JSON files.
* Finally, it exports both the polygon layer (`g_area.shp`) and the point layer (`g_points.shp`) to `data_channel/` so they can be plotted and inspected from R
```{r adjoining1}

source_python(here::here("scripts","python", "identify_distance_property_adjoining_HA.py"))
```

This plot shows the homogeneous areas of Vitacura, allowing us to visualize the spatial partition used in the analysis for that commune.

```{r adjoining2}

g_area <- read_sf("./data_channel/g_area.shp") 

#calles <- opq(bbox = st_bbox(g_area %>%
#                               filter(COMUNA == 15160))) %>%
#  add_osm_feature(key = "highway", 
#                  value = c("residential", "living_street",
#                            "unclassified",
#                            "service", "footway")) %>%
#  osmdata_sf()

g_area %>%
  filter(COMUNA == 15160) %>%
  ggplot() +
#  geom_sf(data = calles$osm_lines,
#          inherit.aes = FALSE,
#          color = "darkgrey",
#          size = .3,
#          alpha = 1) +
  geom_sf(fill = "green",
          alpha = 0.3,
          color = "black",
          linewidth = 0.5) +
  labs(x = "longitud",
       y = "latitud") +
  theme_minimal() +
  theme(axis.title = element_text(size = 12),
        plot.background = element_rect(fill = "white", color = NA),
        aspect.ratio = 1) +
  coord_sf(datum = st_crs(g_area))
```

The next script assigns each homogeneous area to the ZCS with which it has the largest overlap. It reads both shapefiles, harmonizes coordinate systems, keeps residential homogeneous areas, computes polygon intersections, and then stores the dominant ZCS match for each homogeneous area in an `.rds` file. That is, we do the same as with the other python scripts. But we 

```{r ha-within-zcs }
#library(sf)
#library(dplyr)
#library(stringr)
#library(ggplot2)
#library(ggiraph)
#library(plotly)
#library(rdrobust)
#library(fixest)
#library(tidyverse)
#library(rddensity)
#library(rdrobust)
#library(QTE.RD)
#library(data.table)
#library(readxl)
#library(binsreg)

# Functions ---------------------------------------------------------------

#options(modelsummary_factory_default = 'kableExtra')
sf_use_s2(FALSE)

# Zonas de caracteristicas similares ----------------------------------------------------

df_zcs <- read_sf("./raw/zcs/ZCS GRAN SANTIAGO.shp")
df_zcs[,c(6, 9)] <- NULL
df_zcs <- st_set_crs(df_zcs, "EPSG:32719")
df_zcs <- st_transform(df_zcs, 4326)
#df_zcs <- df_zcs[df_zcs$COMUNA == "Vitacura",]
# df_zcs$adj_zcs <- st_touches(df_zcs, df_zcs)
# df_zcs$adj_zcs_number <- sapply(df_zcs$adj_zcs, FUN = function (x) length(x))
# df_zcs <- df_zcs[df_zcs$adj_zcs_number > 0,]
df_zcs$id <- 1:nrow(df_zcs)
df_zcs$ZONA <- paste0(df_zcs$COMUNA, "-", df_zcs$ZONA)

# Areas homogeneas --------------------------------------------------------

df_ah <- read_sf("./raw/homogeneous_areas/gran_stgoPolygon.shp")
df_ah <- df_ah %>%
  filter(USO == "H")
#df_ah <- df_ah[df_ah$NOM_COMUNA == "VITACURA",]
df_ah <- st_transform(df_ah, 4326)
df_ah$adj_AH <- st_touches(df_ah, df_ah)
df_ah$adj_AH_number <- sapply(df_ah$adj_AH, FUN = function (x) length(x))
df_ah <- df_ah[df_ah$adj_AH_number > 0,]
df_ah$id <- 1:nrow(df_ah)
df_ah$adj_AH <- st_touches(df_ah, df_ah)

df_ah$area <- NA
df_ah$ZONA <- NA

i <- 1

for (i in 1:nrow(df_ah)){
  
  print(i)
  
  df_intersect <- st_intersection(df_ah[i,], df_zcs)
  df_intersect$area <- as.numeric(st_area(df_intersect))
  df_intersect <- arrange(df_intersect, desc(area))
  #df_intersect <- df_intersect[1, c("CMN_AH", "ZONA", "area")]
  #df_intersect$geometry <- NULL
  
  df_ah$ZONA[i] <- df_intersect$ZONA.1[1]
  df_ah$area[i] <- df_intersect$area[1]
  
}

df <- df_ah[,c("CMN_AH", "ZONA", "area")]
df$geometry <- NULL
df <- arrange(df, CMN_AH, desc(area))
df$area <- NULL
df <- df[!duplicated(df$CMN_AH),]
df <- df[complete.cases(df),]

saveRDS(df, "./data_channel/ah_within_zcs.rds")
```

